Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-03-22 analysis/paper/paper.Rmd
updated the credit authorship

>>>>

# CRediT authorship contribution statement
Gayoung Park: Software, Validation, Formal analysis, Resources, Data curation,  Writing - original draft, Writing - Review & Editing, Visualization, Project administration.

Marlize Lombard: Conceptualization, Methodology, Formal analysis, Writing - Review & Editing, Supervision

Ben Marwick: Software, Validation, Formal analysis, Investigation, Writing - Review & Editing, Visualization, Supervision
